Supplemental Materials, Methods and Results

### 2021-05-10 ms.Rmd
Fixes to MS, but should have 1st draft of everything now

Sexual selection is expected to favour more conspicuous dymamic sexual signals in Hawaii under relaxed predation because higher predation should favour cryptic signals whereas greater conspicuousness of sexual signals should be selected in social contexts. In support of this prediction, male display colouration exhibited in social contexts (i.e., male-male contests and courtship) was more conspicuous to a conspecific in Hawaii compared with Kenya (Male-Male Contests: Acromatic contrast ($dl$); $F_{`r Population_ConspicDisplayAC$df_num`,`r Population_ConspicDisplayAC$df_denom`}$ = `r Population_ConspicDisplayAC$Fstat`, p = `r p_value(Population_ConspicDisplayAC$p_val)`; Chromatic contrast ($dS$): $F_{`r Population_ConspicDisplayCC$df_num`,`r Population_ConspicDisplayCC$df_denom`}$ = `r Population_ConspicDisplayCC$Fstat`, p = `r p_value(Population_ConspicDisplayCC$p_val)`; Courtship displays: Acromatic contrast ($dl$); $F_{`r Population_ConspicCourtshipAC$df_num`,`r Population_ConspicCourtshipAC$df_denom`}$ = `r Population_ConspicCourtshipAC$Fstat`, p = `r p_value(Population_ConspicCourtshipAC$p_val)`; Chromatic contrast ($dS$): $F_{`r Population_ConspicCourtshipCC$df_num`,`r Population_ConspicCourtshipCC$df_denom`}$ = `r Population_ConspicCourtshipCC$Fstat`, p = `r p_value(Population_ConspicCourtshipCC$p_val)`), and this was  true across all body regions measured (See Supplemental Materials, table S1). Kenyan chameleons from populations where predation is high were significantly more crypic compared to introduced Hawaiian counterparts (Acromatic Contrast between Hawaiian and Kenyan Populations, Male-male contests: $\beta$ = `r robust_ConspicDisplayAC$beta[3]`, 95% CI = `r robust_ConspicDisplayAC_CI$CI_L[3]` to  `r robust_ConspicDisplayAC_CI$CI_U[3]`, df = `r robust_ConspicDisplayAC$df[3]`, t =  `r robust_ConspicDisplayAC$tstat[3]`, p = `r p_value(robust_ConspicDisplayAC$p_Satt[3])`, Courtship: $\beta$ = `r robust_ConspicCourtshipAC_CI$beta[3]`, 95% CI = `r robust_ConspicCourtshipAC_CI$CI_L[3]` to  `r robust_ConspicCourtshipAC_CI$CI_U[3]`, df = `r robust_ConspicCourtshipAC_CI$df[3]`, t =  `r summary(ConspicCourtshipAC)$coefficients[3, "t value"]`, p = `r p_value(robust_ConspicCourtshipAC$p_Satt[3])`, see figure 1a & b).

@@

Local adaptation of sexual signals would result in Hawaiian chameleons being more conspicous to conspecifics in the Hawaiian environment compared to their native Kenyan environment. While it was not possible to conduct common garden experiments to provide definitive tests of local adaptation, our results support the local adaptation hypothesis given that Hawaiian chameleons were more conspicous to other chamleeons in the Hawaiian environment compared to the same chameleons in a Kenyan environment in both social contexts (figure 2; Contrast between Hawaiian lizard on Kenyan vs Hawaiian on Hawaiin background - Male-male contests: Achromatic ($dl$), $\beta$ = `r CI_dis_AC[1,1]`, 95% CI = `r CI_dis_AC[1,2]` to `r CI_dis_AC[1,3]`, p = `r p_displ_AC`, Chromatic ($dS$) $\beta$ = `r CI_Disp_CC[1,1]`, 95% CI = `r CI_Disp_CC[1,2]` to `r CI_Disp_CC[1,3]`, p = `r p_displ_CC`; Courtship: Achromatic ($dl$), $\beta$ = `r CI_AC_Courtship[1,1]`, 95% CI = `r CI_AC_Courtship[1,2]` to `r CI_AC_Courtship[1,3]`, p = `r p_courtship_AC`, Chromatic ($dS$) $\beta$ = `r CI_CC_Courtship[1,1]`, 95% CI = `r CI_CC_Courtship[1,2]` to `r CI_CC_Courtship[1,3]`, p = `r p_courtship_CC`).

>>>>

Sexual selection is expected to favour more conspicuous dymamic sexual signals in Hawaii under relaxed predation because higher predation should favour cryptic signals whereas greater conspicuousness of sexual signals should be selected in social contexts. In support of this prediction, male display colouration exhibited in social contexts (i.e., male-male contests and courtship) was more conspicuous to a conspecific in Hawaii compared with Kenya (Male-Male Contests: Acromatic contrast ($dl$); $F_{`r Population_ConspicDisplayAC$df_num`,`r Population_ConspicDisplayAC$df_denom`}$ = `r Population_ConspicDisplayAC$Fstat`, p = `r p_value(Population_ConspicDisplayAC$p_val)`; Chromatic contrast ($dS$): $F_{`r Population_ConspicDisplayCC$df_num`,`r Population_ConspicDisplayCC$df_denom`}$ = `r Population_ConspicDisplayCC$Fstat`, p = `r p_value(Population_ConspicDisplayCC$p_val)`; Courtship displays: Acromatic contrast ($dl$); $F_{`r Population_ConspicCourtshipAC$df_num`,`r Population_ConspicCourtshipAC$df_denom`}$ = `r Population_ConspicCourtshipAC$Fstat`, p = `r p_value(Population_ConspicCourtshipAC$p_val)`; Chromatic contrast ($dS$): $F_{`r Population_ConspicCourtshipCC$df_num`,`r Population_ConspicCourtshipCC$df_denom`}$ = `r Population_ConspicCourtshipCC$Fstat`, p = `r p_value(Population_ConspicCourtshipCC$p_val)`), and this was  true across all body regions measured (See Supplemental Materials). Kenyan chameleons from populations where predation is high were significantly more crypic compared to introduced Hawaiian counterparts (Acromatic Contrast between Hawaiian and Kenyan Populations, Male-male contests: $\beta$ = `r robust_ConspicDisplayAC$beta[3]`, 95% CI = `r robust_ConspicDisplayAC_CI$CI_L[3]` to  `r robust_ConspicDisplayAC_CI$CI_U[3]`, df = `r robust_ConspicDisplayAC$df[3]`, t =  `r robust_ConspicDisplayAC$tstat[3]`, p = `r p_value(robust_ConspicDisplayAC$p_Satt[3])`, Courtship: $\beta$ = `r robust_ConspicCourtshipAC_CI$beta[3]`, 95% CI = `r robust_ConspicCourtshipAC_CI$CI_L[3]` to  `r robust_ConspicCourtshipAC_CI$CI_U[3]`, df = `r robust_ConspicCourtshipAC_CI$df[3]`, t =  `r summary(ConspicCourtshipAC)$coefficients[3, "t value"]`, p = `r p_value(robust_ConspicCourtshipAC$p_Satt[3])`, see figure 1a & b).

@@

Local adaptation of sexual signals would result in Hawaiian chameleons being more conspicous to conspecifics in the Hawaiian environment compared to their native Kenyan environment. While it was not possible to conduct common garden experiments to provide definitive tests of local adaptation, our results support the local adaptation hypothesis given that Hawaiian chameleons were more conspicous to other chameleons in the Hawaiian environment compared to the same chameleons in a Kenyan environment in both social contexts (figure 2; Contrast between Hawaiian lizard on Kenyan vs Hawaiian on Hawaiin background - Male-male contests: Achromatic ($dl$), $\beta$ = `r CI_dis_AC[1,1]`, 95% CI = `r CI_dis_AC[1,2]` to `r CI_dis_AC[1,3]`, p = `r p_displ_AC`, Chromatic ($dS$) $\beta$ = `r CI_Disp_CC[1,1]`, 95% CI = `r CI_Disp_CC[1,2]` to `r CI_Disp_CC[1,3]`, p = `r p_displ_CC`; Courtship: Achromatic ($dl$), $\beta$ = `r CI_AC_Courtship[1,1]`, 95% CI = `r CI_AC_Courtship[1,2]` to `r CI_AC_Courtship[1,3]`, p = `r p_courtship_AC`, Chromatic ($dS$) $\beta$ = `r CI_CC_Courtship[1,1]`, 95% CI = `r CI_CC_Courtship[1,2]` to `r CI_CC_Courtship[1,3]`, p = `r p_courtship_CC`).

### 2021-05-10 supp.Rmd
Fixes to MS, but should have 1st draft of everything now

The magnitude of chromatic contrast differences between Hawaiian chamaleons against their own environment and a Kenyan enviroment did depend on the body region (Male-male display: $F_{`r intearction_CC_Disp$df_num`, `r intearction_CC_Disp$df_denom`}$ = `r intearction_CC_Disp$Fstat`, p = `r p_value(intearction_CC_Disp$p_val)`; Courtship Display: $F_{`r intearction_CC_Court$df_num`, `r intearction_CC_Court$df_denom`}$ = `r intearction_CC_Court$Fstat`, p = `r p_value(intearction_CC_Court$p_val)`, Figure \@ref(fig:FigS4)A & C & Table \@ref(tab:table7)). However, in all cases there was a tendeny for all body regions of Hawaiian populations to decrease in average contrast when viewed by a conspecific against a Hawaiian versus Kenyan background (Figure \@ref(fig:FigS4)A & C), and only some body regions showed a significant decrease (Table \@ref(tab:table8)).

The magnitude of achromatic contrast, showed a significant overall decrease in achromatic contrast when viewed by conspevcifics against a Kenyan background (Overall Background Effect: Male-male display, $F_{`r background_AC_Disp$df_num`, `r background_AC_Disp$df_denom`}$ = `r background_AC_Disp$Fstat`, p = `r p_value(background_AC_Disp$p_val)`, Courtship Display, $F_{`r background_AC_Court$df_num`, `r background_AC_Court$df_denom`}$ = `r background_AC_Court$Fstat`, p = `r p_value(background_AC_Court$p_val)`, Figure \@ref(fig:figS4)B & D along with & Table \@ref(tab:table7)), and there were significant differences among body regions (Overall Body Region Effect: Male-male display, $F_{`r BodyRegion_AC_Disp$df_num`, `r BodyRegion_AC_Disp$df_denom`}$ = `r BodyRegion_AC_Disp$Fstat`, p = `r p_value(BodyRegion_AC_Disp$p_val)`, Courtship Display, $F_{`r BodyRegion_AC_Court$df_num`, `r BodyRegion_AC_Court$df_denom`}$ = `r BodyRegion_AC_Court$Fstat`, p = `r p_value(BodyRegion_AC_Court$p_val)`, Figure \@ref(fig:figS4)B & D along with & Table \@ref(tab:table7)).

@@

```{r table7, tab.cap = "Estimated model parameters, standard errors (SE), degrees of freedom (df) along with 95% confidence interval for each parameter. Main effects and interaction models are presented. Only main effect models are presented for achromatic contrast (see text for details), whereas interaction models are presented for chromatic contrast. Pairwise contrasts are presented for chromatic contrast models (see Table 8) for ease of interpretation."}
table7 <- rbind(robust_localAdapt_DispBgrdAC,
                robust_DispBgrdCC,
                robust_CourtshipAC,
                robust_CourtshipCC) %>% as.data.frame()

@@

Table7 <- flextable(table7) %>% table_style10()

```{r table8, tab.cap = "Pairwise Wald F tests comparing changes in chromatic contrast between different body regions for Hawaiian lizards against both Hawaiian and Kenyan backgrounds during male-male and courtship displats. F statistic, degrees of freedom (DF) and p-values are provided (p). A bonferroni correction to p-value is also provided to control for multiple testing. See Table 7 for model estimates."}
tab8 <- rbind(result_DisplayBgrd_pop_back_regionCC,
              result_CourtshipBgrd_pop_back_BR_CC) %>%  as.data.frame()

>>>>

The magnitude of chromatic contrast differences between Hawaiian chamaleons against their own environment and a Kenyan enviroment did depend on the body region (Male-male display: $F_{`r intearction_CC_Disp$df_num`, `r intearction_CC_Disp$df_denom`}$ = `r intearction_CC_Disp$Fstat`, p = `r p_value(intearction_CC_Disp$p_val)`; Courtship Display: $F_{`r intearction_CC_Court$df_num`, `r intearction_CC_Court$df_denom`}$ = `r intearction_CC_Court$Fstat`, p = `r p_value(intearction_CC_Court$p_val)`, Figure \@ref(fig:FigS4)A & C & Table \@ref(tab:tableS7)). However, in all cases there was a tendeny for all body regions of Hawaiian populations to decrease in average contrast when viewed by a conspecific against a Hawaiian versus Kenyan background (Figure \@ref(fig:FigS4)A & C), and only some body regions showed a significant decrease (Table \@ref(tab:tableS8)).

The magnitude of achromatic contrast, showed a significant overall decrease in achromatic contrast when viewed by conspevcifics against a Kenyan background (Overall Background Effect: Male-male display, $F_{`r background_AC_Disp$df_num`, `r background_AC_Disp$df_denom`}$ = `r background_AC_Disp$Fstat`, p = `r p_value(background_AC_Disp$p_val)`, Courtship Display, $F_{`r background_AC_Court$df_num`, `r background_AC_Court$df_denom`}$ = `r background_AC_Court$Fstat`, p = `r p_value(background_AC_Court$p_val)`, Figure \@ref(fig:FigS4)B & D along with Table \@ref(tab:tableS7)), and there were significant differences among body regions (Overall Body Region Effect: Male-male display, $F_{`r BodyRegion_AC_Disp$df_num`, `r BodyRegion_AC_Disp$df_denom`}$ = `r BodyRegion_AC_Disp$Fstat`, p = `r p_value(BodyRegion_AC_Disp$p_val)`, Courtship Display, $F_{`r BodyRegion_AC_Court$df_num`, `r BodyRegion_AC_Court$df_denom`}$ = `r BodyRegion_AC_Court$Fstat`, p = `r p_value(BodyRegion_AC_Court$p_val)`, Figure \@ref(fig:FigS4)B & D along with Table \@ref(tab:tableS7)).

@@

```{r tableS7, tab.cap = "Estimated model parameters, standard errors (SE), degrees of freedom (df) along with 95% confidence interval for each parameter. Main effects and interaction models are presented. Only main effect models are presented for achromatic contrast (see text for details), whereas interaction models are presented for chromatic contrast. Pairwise contrasts are presented for chromatic contrast models (see Table 8) for ease of interpretation."}
table7 <- rbind(robust_localAdapt_DispBgrdAC,
                robust_DispBgrdCC,
                robust_CourtshipAC,
                robust_CourtshipCC) %>% as.data.frame()

@@

Table7 <- flextable(table7) %>% table_style10()
Table7
```

```{r tableS8, tab.cap = "Pairwise Wald F tests comparing changes in chromatic contrast between different body regions for Hawaiian lizards against both Hawaiian and Kenyan backgrounds during male-male and courtship displats. F statistic, degrees of freedom (DF) and p-values are provided (p). A bonferroni correction to p-value is also provided to control for multiple testing. See Table 7 for model estimates."}
tab8 <- rbind(result_DisplayBgrd_pop_back_regionCC,
              result_CourtshipBgrd_pop_back_BR_CC) %>%  as.data.frame()
